### 2023-03-31 reachable-resilience.tex
up

The problem is however unfortunately undecidable in general.

@@

\begin{proof}
Taking $\Safe = 0$, $\Bad = S \setminus 0$, it follows the state resilience problem is equivalent
to reachability of $0$.
\end{proof}

>>>>

Unfortunately however the problem is undecidable in general.

@@

\begin{proof}
Taking $\Safe = \{ 0 \}$, $\Bad = S \setminus 0$, it follows the state resilience problem is equivalent
to reachability of $0$. Since reachability of $0$ is undecidable for Reset VASS, we conclude.
\end{proof}
